Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-11 paper/main.tex
[issue 2.27] add sdss feature maps

@@

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_galaxy_original.pdf}
    \caption{Input (5 bands$\times44\times44$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_galaxy_conv11.pdf}
    \caption{Layer 1 (32 maps$\times40\times40$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_galaxy_conv21.pdf}
    \caption{Layer 3 (64 maps$\times20\times20$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_galaxy_conv31.pdf}
    \caption{Layer 6 (128 maps$\times10\times10$)}
  \end{subfigure}
  \caption{
\changed{
    Similar to Figure~\ref{fig:galaxy_activations} but for a galaxy in the
    SDSS data set.
}
    }
  \label{fig:sdss_galaxy_activations}
\end{figure*}

\begin{figure*}
  \centering
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_star_original.pdf}
    \caption{Input (5 bands$\times44\times44$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_star_conv11.pdf}
    \caption{Layer 1 (32 maps$\times40\times40$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_star_conv21.pdf}
    \caption{Layer 3 (64 maps$\times20\times20$)}
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.24\linewidth}
  \centering
    \includegraphics[width=\textwidth]{figures/sdss_star_conv31.pdf}
    \caption{Layer 6 (128 maps$\times10\times10$)}
  \end{subfigure}
  \caption{
\changed{
    Similar to Figure~\ref{fig:sdss_galaxy_activations} but for a star in the
    SDSS data set.
}
    }
  \label{fig:sdss_star_activations}
\end{figure*}

@@

\changed{
Figures~\ref{fig:sdss_galaxy_activations} and \ref{fig:sdss_star_activations}
show the activations when images of a galaxy and a star are fed into the network. 
Similarly to Figures~\ref{fig:galaxy_activations} and \ref{fig:star_activations}
in Section~\ref{sec:results_cfht},
the feature maps show hierarchical abstraction from low-level features in the
first convolutional layer to high-level features in the subsequent layers.
This hierarchical abstraction is what enables ConvNets to learn morphological
features automatically from images.
}
